Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
more space savings

\para{Abstract topology}
Abstract topologies in \sysname define structural and role-based invariants that capture a collection of concrete networks. These invariants are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities and connectivity.
%
We designed these abstractions to be able to precisely capture most real network topologies, while being amenable to the fault tolerance analysis and configuration synthesis that is done by our compiler.

@@

The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs. On its own, this abstraction loses a lot of information about the underlying structure of the concrete network, making it difficult to reason precisely about fault-tolerance.
%which would hinder a useful analysis of its fault-tolerance.
For example, with this abstraction any spine router in a concrete network may or may not be connected to any aggregator router.
%
In order to refine the abstraction to capture more precisely the kinds of concrete networks of interest,
we introduce several additional concepts. The first is the idea of a topology hierarchy captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into a number of smaller pods.
The second is a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
with a symbolic variable (\EG, $e1, e2, \ldots$) that denotes a constraint on the number of edges (and nodes) that may appear in any given concrete network. Operators can capture concrete network invariants by adding constraints on the symbolic variables using logical formula.

@@

  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules.}
  \label{fig:inference-rules}
  %\vspace{-1em}
\end{figure*}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figures/analysis}
  \end{center}
  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
  \label{fig:example-inference}
  \vspace{-1em}
\end{figure}

@@

  \begin{center}
  \includegraphics[width=\columnwidth]{figures/configs}  
  \end{center}
  \vspace{-1em}
  \caption{Spine template and concrete configurations (left), and evolution friendly templates (right).}
  \label{fig:bgp-configs}
\end{figure}

@@

\begin{defn}
Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$. Intuitively $m \geq_{rank} n$ means that paths ending at PG node $m$ are no better in terms of preference than paths ending at $n$.
%
\end{defn}
\noindent
%

@@

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l | c | c | c |}
      \hline
      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachability} & \textbf{K-paths} \\ \hline
      Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
      Facebook~\cite{facebook-fattree} & & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & & \cmark & \cmark \\ \hline
      VL2~\cite{vl2-fattree} & & & \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \xmark \\ \hline
      Dcell~\cite{dcell} & $k$ & \cmark & \xmark \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \caption{Fault-tolerance analysis precision.}
  \label{fig:analysis-precision}
\end{figure}

@@

\begin{figure}[t!]
  \subcaptionbox{Datacenter}
    {\includegraphics[width=.49\columnwidth]{figures/Fattree-time.png}}
  \subcaptionbox{Backbone}
    {\includegraphics[width=.49\columnwidth]{figures/backbone-time.png}} \\
  \caption{Concrete vs. Abstract Generation Time. \label{fig:compilation-times}}
  \vspace{-1em}
\end{figure}

\begin{figure}[t!]
  \subcaptionbox{Datacenter}
    {\includegraphics[width=.49\columnwidth]{figures/Fattree-analysis-time.png}}
  \subcaptionbox{Backbone}
    {\includegraphics[width=.49\columnwidth]{figures/backbone-analysis-time.png}} \\
  \caption{Abstract Generation Time by Phase. \label{fig:abstract-breakdown}}
  \vspace{-1em}
\end{figure}

>>>>

\para{Abstract topology}
Abstract topologies in \sysname define structural and role-based invariants that describe a collection of concrete networks. These invariants are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
%
We designed these abstractions to be able to precisely capture many real network topologies, while also being amenable to fault-tolerance analysis and configuration synthesis.

@@

The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs. On its own, this abstraction loses a lot of information about the structure of concrete networks, making it difficult to reason precisely about fault-tolerance.
%which would hinder a useful analysis of its fault-tolerance.
For example, with this abstraction any spine router in a concrete network may or may not be connected to any aggregator router.
%
In order to refine the abstraction to capture more precisely the kinds of concrete networks of interest,
we introduce several additional concepts. The first is the idea of a topology hierarchy captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into a number of smaller pods.
The second is a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
with a symbolic variable (\EG, $e1, e2, \ldots$) that denotes a constraint on the number of edges (and nodes) that may appear in any given concrete network. Operators can capture concrete network invariants by adding constraints on the symbolic variables using logical formula.

@@

  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules.}
  \label{fig:inference-rules}
  \vspace{-1.4em}
\end{figure*}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth]{figures/analysis}
  \end{center}
  \vspace{-1.4em}
  \caption{Abstract disjoint path analysis for global prefixes. \label{fig:compilation-times}}
  \label{fig:example-inference}
  \vspace{0em}
\end{figure}

@@

  \begin{center}
  \includegraphics[width=\columnwidth]{figures/configs}  
  \end{center}
  \vspace{-1em}
  \caption{Spine template and concrete configurations (left), and evolution-friendly templates (right).}
  \label{fig:bgp-configs}
\end{figure}

@@

\begin{defn}
Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$. Intuitively $m \geq_{rank} n$ means that paths ending at PG node $m$ are no better than paths ending at $n$.
%
\end{defn}
\noindent
%

@@

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l | c | c | c |}
      \hline
      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachable} & \textbf{K-paths} \\ \hline
      Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
      Facebook~\cite{facebook-fattree} & & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & & \cmark & \cmark \\ \hline
      VL2~\cite{vl2-fattree} & & & \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \xmark \\ \hline
      Dcell~\cite{dcell} & $k$ & \cmark & \xmark \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \vspace{-.6em}
  \caption{Fault-tolerance analysis precision.}
  \label{fig:analysis-precision}
  \vspace{-1em}
\end{figure}

@@

\begin{figure}[t!]
  \subcaptionbox{Datacenter}
    {\includegraphics[width=.49\columnwidth]{figures/Fattree-time.png}}
  \subcaptionbox{Backbone}
    {\includegraphics[width=.49\columnwidth]{figures/backbone-time.png}} \\
  \vspace{-.6em}
  \caption{Concrete vs. Abstract Generation Time. \label{fig:compilation-times}}
  \vspace{-1em}
\end{figure}

\begin{figure}[t!]
  \subcaptionbox{Datacenter}
    {\includegraphics[width=.49\columnwidth]{figures/Fattree-analysis-time.png}}
  \subcaptionbox{Backbone}
    {\includegraphics[width=.49\columnwidth]{figures/backbone-analysis-time.png}} \\
  \vspace{-.6em}
  \caption{Abstract Generation Time by Phase. \label{fig:abstract-breakdown}}
  \vspace{-1em}
\end{figure}
